Software Citation Principles

### 2016-04-05 sc-principles/software-citation-principles.tex

\item ``Repository'' refers to public software repositories such as Astronomy
Source Code Library (ASCL)~\cite{ascl}, GitHub, Netlib, Comprehensive R Archive
Network (CRAN), institutional repositories.

@@

\item ``Domain group'' includes bioCADDIE~\cite{bioCADDIE}, Computational
Infrastructure for Geodynamics (CIG)~\cite{CIG}, etc..

\item ``Unique identifier'' refers to identifiers such as a DOI, ARK, or PURL.

\item``Reproduce'' can mean reproduction, replication, verification, validation,
repeatability, and\slash or utility.
\end{itemize}

>>>>

@@

\item ``Domain group\slash library\slash archive'' includes the Astronomy Source Code Library (ASCL)~\cite{ascl}, 
bioCADDIE~\cite{bioCADDIE}, Computational Infrastructure for Geodynamics (CIG)~\cite{CIG}, libraries, institutional archives, etc.

\item ``Repository'' refers to public software repositories such as GitHub, Netlib, Comprehensive R Archive
Network (CRAN), and institutional repositories.

\item ``Unique identifier'' refers to unique, persistent, and machine-actionable identifiers such as a DOI, ARK, or PURL.

\item ``Reproduce'' can mean actions focused on reproduction, replication, verification, validation, repeatability, and\slash or utility.

\item ``Citation manager`` refers to people and organizations that create scholarly reference 
management software and websites including Zotero, Mendeley, EndNote, RefWorks, BibDesk, etc., 
that manage citation information and semi-automatically insert those citations into research products.
